Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-02 doc/JFLA2022/paper.tex
jfla: Move snippets to a separate directory
jfla: Build snippets separately
jfla: Rebuild snippets
jfla: Minor tweaks

\usepackage{texments}
%%% for movies by alectryon
\usepackage{../movies/snippets/assets/alectryon}
\usepackage{../movies/snippets/assets/pygments}
%%% One hypothesis per line 
\makeatletter
\renewcommand{\alectryon@hyps@sep}{\alectryon@nl}
\makeatother

%%% \snippets{A,B,C,…} inputs a series of snippets as one block (with \itemsep
%%% between them).  A, B, C should be paths to files in movies/snippets/.
\usepackage{etoolbox}
\makeatletter
\newcommand{\inputsnippets}[1]
  {{\setlength{\itemsep}{1pt}\setlength{\parsep}{0pt}% Adjust spacing
    \alectryon@copymacros\begin{io}
      \forcsvlist{\item\@inputsnippet}{#1}
    \end{io}}}
\let\input@old\input % Save definition of \input
\newcommand{\@inputsnippet}[1]
  {{\renewenvironment{alectryon}{}{}% Skip \begin{alectryon} included in snippet
    \input@old{#1}}}
\makeatother

@@

\begin{theorem}
  Let $\mu$ be any ordinal strictly less than $\epsilon_0$.
  There is no function mapping hydras to the segment $[0,\mu)$, which could be used as a measure for  proving the termination of  all hydra battles.\label{thm3}
\end{theorem}

\TODO[Clément]{Is there a word missing above?}
Considering measures applicable to \emph{all} battles allowed us to
focus on battles where the hydra can make an arbitrary number of copies at any time, which made our proof by contradiction artificially easier.
Unfortunately, the examples  most commonly shown in the litterature
(see for instance~\cite{KP82, bauer2008, BauerHydra}) 
assume that the hydra grows $n$ copies at step $n$ of the game, which is incompatible with our proof.

@@

 \begin{figure}[h]
 \inputsnippets{HprimeDef}
\caption{$H'$ definition with the \texttt{coq-equations}
 plug-in~\cite{sozeau:hal-01671777}}
\label{fig:Hprime}
\end{figure}

@@

\TODO[Clément]{Highlight `Equations' and remove `omega' highlighting; change theme to something less garish}

@@

  \begin{figure}[h]
    \centering
    \fbox{
      \begin{minipage}[h]{1.0\linewidth}
        \inputsnippets{Ex42}
      \end{minipage}}
    \caption{A simple proof by computation}
    \label{fig:Ex42E0}
  \end{figure}

@@

\inputsnippets{Ex42a}

@@

\inputsnippets{Ex42b}

@@

\inputsnippets{Ex42d, Ex42c, Ex42e}

>>>>

\usepackage{texments}
%%% for movies by alectryon
\usepackage{./assets/alectryon}
\usepackage{./assets/pygments}
%%% One hypothesis per line 
\makeatletter
\renewcommand{\alectryon@hyps@sep}{\alectryon@nl}
\makeatother

%%% \snippets{A,B,C,…} inputs a series of snippets as one block (with \itemsep
%%% between them).  A, B, C should be paths to files in snippets/.
\usepackage{etoolbox}
\makeatletter
\newcommand{\inputsnippets}[1]
  {{\setlength{\itemsep}{1pt}\setlength{\parsep}{0pt}% Adjust spacing
    \alectryon@copymacros\begin{io}
      \forcsvlist{\item\@inputsnippet}{#1}
    \end{io}}}
\let\input@old\input % Save definition of \input
\newcommand{\@inputsnippet}[1]
  {{\renewenvironment{alectryon}{}{}% Skip \begin{alectryon} included in snippet
    \input@old{snippets/#1}}}
\makeatother

@@

\begin{theorem}
  Let $\mu$ be any ordinal strictly less than $\epsilon_0$.
  There is no function mapping hydras to the segment $[0,\mu)$ that could be used as a measure for  proving the termination of  all hydra battles.\label{thm3}
\end{theorem}

Considering measures applicable to \emph{all} battles allowed us to
focus on battles where the hydra can make an arbitrary number of copies at any time, which made our proof by contradiction artificially easier.
Unfortunately, the examples  most commonly shown in the litterature
(see for instance~\cite{KP82, bauer2008, BauerHydra}) 
assume that the hydra grows $n$ copies at step $n$ of the game, which is incompatible with our proof.

@@

 \begin{figure}[h]
 \inputsnippets{Hprime/HprimeDef}
\caption{$H'$ definition with the \texttt{coq-equations}
 plug-in~\cite{sozeau:hal-01671777}}
\label{fig:Hprime}
\end{figure}

@@

\TODO[Clément]{Could we use a font with ligatures?}

@@

  \begin{figure}[h]
    \centering
    \fbox{
      \begin{minipage}[h]{1.0\linewidth}
        \inputsnippets{E0/Ex42}
      \end{minipage}}
    \caption{A simple proof by computation}
    \label{fig:Ex42E0}
  \end{figure}

@@

\inputsnippets{Schutte/Ex42a}

@@

\inputsnippets{Schutte/Ex42b}

@@

\inputsnippets{Schutte/Ex42d, Schutte/Ex42c, Schutte/Ex42e}
